\documentclass{article}
\pagestyle{empty}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{
  a4paper,
  top=10mm,
  left=15mm,
  total={180mm, 277mm}
}
\usepackage{fontawesome}
\newlength{\sectionspacing}
\setlength{\sectionspacing}{0.2cm}
\newcommand{\cvcompany}[2]{%
  \noindent{\bf #1}, #2\newline
}
\newcommand{\cvrole}[2]{%
  \noindent{\bf #1} \hfill #2\newline
}

\begin{document}
\noindent
\begin{minipage}[t]{0.64\textwidth}
    \vspace{0pt}
    \raggedright
    {\Huge Artem Kislovskiy}\\[0.2cm]
    {\Large Software Engineer}
\end{minipage}
\hfill
\begin{minipage}[t]{0.36\textwidth}
  \vspace{0pt}
  \raggedright
  \begin{tabular}{@{}cl@{}}
    \faMapMarker  & Avenue de la Chabliere, 22 \\
                  & 1004 Lausanne \\
    \faFlag       & Permit B \\
    \faEnvelope   & \href{mailto:kislovskiy@proton.me}{kislovskiy@proton.me} \\
    \faPhone      & +41 78 779 83 99 \\
    \faLinkedin   & \href{https://linkedin.com/in/artemkislovskiy}{linkedin.com/in/artemkislovskiy} \\
    \faGithub     & \href{https://github.com/kislovskiy}{github.com/kislovskiy}
  \end{tabular}
\end{minipage}
\vspace{\sectionspacing}

A computational physicist turned backend engineer with 6 years of experience building reliable data infrastructure and tooling at internet scale.
Drove the early adoption of cloud, Kubernetes, and CI/CD, then codified lessons with platform teams
into reusable patterns for a smoother organization-wide rollout.
Fluent across six languages: Scala/Java for data and concurrency, Python for ML and tooling, Go \& TypeScript for Grafana extensions, Bash for scripting, applying each where it excels rather than defaulting to the familiar.

\vspace{\sectionspacing}
\begin{tabular}{ll}
  Languages:      & Python, Scala, Java, Go, TypeScript, Bash \\
  Frameworks:     & Akka/Pekko, SpringBoot, Apache Spark, TensorFlow, PyTorch \\
  Platform:       & Kubernetes, Docker, AWS, Terraform, Jenkins, GitHub Actions, Grafana, Prometheus, Splunk \\
  Certifications: & AWS Certified Solutions Architect – Associate \\
                  & Certified Kubernetes Application Developer – CKAD
\end{tabular}
\vspace{\sectionspacing}
\vspace{\sectionspacing}

\noindent
Experience\newline
\cvcompany{Verisign}{Fribourg, Switzerland}
\cvrole{Software Engineer -- Data Engineering Team}{Sep 2023 --- Apr 2026}
\vspace{-\topsep}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \item Built the company's first Jenkins CI/CD pipeline for Kubernetes, automating security approvals, vulnerability scans, artifact signing, and environment promotion.
    Cut certification time for three teams from days to under an hour per release, and reduced artifact metadata propagation from three hours to five minutes.
    \item Led the migration from Akka to Pekko to reduce licensing costs. Starting from a hackathon proof of concept, produced a technical analysis, validated the approach with industry contacts, and migrated core apps to production without disruption. Built a zero‑downtime migration using a simple build tool to compile both flavors from a single Akka source. The implementation is selected at startup, enabling safe blue/green rollout with instant rollback.
    \item As one of two engineers, owned data ingestion and integrity organization-wide, processing 500\,000 records per second in real time. Operating across six languages sharpened fluency and reliability as a cross‑stack generalist.
\end{itemize}

\cvrole{Software Engineer – NameStudio API Team (\href{https://namestudioapi.com}{namestudioapi.com})}{Jan 2020 --- Sep 2023}
\vspace{-\topsep}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \item Eliminated a Python-Java bottleneck by migrating machine learning model serving to TensorFlow Serving, unifying training and inference, and accelerating the ML experimentation cycle.
    Reduced CPU utilization at equivalent load, validated through a full Gatling load-test suite, and deployed in parallel with full production stability. The decoupled architecture enabled GPU-based compute migration, seamless addition of ML microservices, and straightforward LLM integration. Documented the architecture, enabling other engineers to onboard and contribute independently.
    \item Built A/B testing infrastructure and Apache Spark pipelines that produced a quantified proof of the API's impact on .COM and .NET domain registrations. Designed a mathematical model to correlate server logs and domain data, delivering Tableau dashboards and daily PDF reports for engineering, product, and marketing.
\end{itemize}

\vspace{\sectionspacing}
\cvcompany{EPFL}{Lausanne, Switzerland}
\cvrole{Research Assistant -- Unsteady Flow Diagnostics Laboratory}{Sep 2018 --- Nov 2019}
\vspace{-\topsep}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \item Applied fluid dynamics and machine learning to develop a convolutional neural network that removes artifacts from particle image velocimetry data. Served as Teaching Assistant for Aerodynamics, creating exercises, assessments, training materials.
\end{itemize}

\vspace{\sectionspacing}
\noindent
Education\newline
{\bf EPFL} École Polytechnique Fédérale de Lausanne \hfill Sep 2018 --- Nov 2019 \\
Doctoral Candidate, Doctoral Program in Mechanics (EDME) - transitioned to industry before completion.\newline
\noindent
{\bf MIPT} Moscow Institute of Physics and Technology\newline
M.Sc. with Honors in Applied Mathematics and Physics (Computational Fluid Dynamics) \hfill Sep 2016 --- Jul 2018\newline
B.Sc. in Applied Mathematics and Physics \hfill Sep 2012 --- Jul 2016

\vspace{\sectionspacing}
\noindent
Volunteering\newline
\cvcompany{EuroPython Society}{Agnesberg, Sweden}
\cvrole{Vice Chair}{Oct 2023 --- Nov 2024}
\vspace{-\topsep}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{-30pt}
    \item As Vice Chair and sponsorship lead, secured EuroPython funding, sourced partners, closed deals, and built a tracking system with a three-person volunteer team.
\end{itemize}

\end{document}
